Responses to reviewers' comments and list of modifications done\\ on paper SORO226\\ \LARGE{\textbf{Grounding the interaction: anchoring situated discourse in everyday human-robot interaction}}

### 2011-07-16 cover_letter.tex
Added a reference to Zender's work
Addressed comment on 'Give examples of OpenCyc alignement

Below follow our answers to the reviewers’ comments and suggestions. Each answer also indicates the changes made in the paper to address the reviewer’s concern. An important number of language corrections are made, and the paper is proof-read by a native English speaker.

@@

@@

>>>>

Below follow our answers to the reviewersÕ comments and suggestions. Each answer also indicates the changes made in the paper to address the reviewerÕs concern. An important number of language corrections are made, and the paper is proof-read by a native English speaker.

@@

Numerous predicates in {\tt commonsense.oro.owl} are defined in the 
OpenCyc namespace: {\tt farFrom, near, hold-Underspecified, objectFoundInLocation}.

Similarly, most of the upper classes in the ontology belong to OpenCyc 
(like {\tt SpatialThing, PartiallyTangible, TemporalThing}...).

Overall, about 50 entites (on the >180 defined in {\tt commonsense.oro.owl}) 
come from OpenCyc.

Since most of the upper classes are OpenCyc concepts, this should 
guarantee to a certain extend the alignment of our ontology with other ontologies.

@@

A reference to Zender's work has been added to the \emph{Related work} section.
